Context Aware Virtual Assistant with Case-Based Conflict Resolution in Multi-User Smart Home Environment

### 2018-01-30 Paper/Paper.tex
удалено:       Paper/Images/CBR.png 	удалено:       Paper/Images/CBR1.png 	удалено:       Paper/Images/CBRefficiencychart.png 	удалено:       Paper/Images/DM.png 	удалено:       Paper/Images/Evaluation Tests.png 	удалено:       Paper/Images/FNN.png 	удалено:       Paper/Images/GA.png 	удалено:       Paper/Images/HL.png 	удалено:       Paper/Images/Instructions.jpg 	удалено:       Paper/Images/RBR.png 	удалено:       Paper/Images/arch-legend.png 	изменено:      Paper/Images/arch.png 	удалено:       Paper/Images/chartGA.png 	удалено:       Paper/Images/mahalanobis.png 	удалено:       Paper/Image

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{llncsdoc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{Images/}}
\begin{document}
    \title{Context Aware Virtual Assistant with
    Case-Based Conflict Resolution in
    Multi-User Smart Home Environment}
    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Quinde \inst{2} \inst{3} \and Kenzhegali Nurgaliyev \inst{1}}
    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}
    \and Department of Industrial and Systems Engineering, Universidad de Piura, Av. Ramon Mujica 131, Urb. San Eduardo, Piura, Peru\\
    \email{mario.quinde@udep.pe}}
    \maketitle
    \begin{abstract}
        In this work we will examine and develop a Virtual Assistant that is used as a control
        interface of the Smart Home environment in the Farm Side Middlesex University laboratory.
        Specifically, the system is
        constructed to give multiple users ability to control devices by voice or text commands through the dialogue
        interface.
        The main purpose of the research is to create user friendly interface with adaptive context aware
        Case-Based conflict resolution system.
        In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
        recognition and voice generation instruments were used to implement natural dialogue model of interactions with users.
        Further, a set of randomised double-blinded
        evaluation tests were established.
    \end{abstract}
    \begin{keywords}
        Case-Based Reasoning, Context Awareness, Multiple User systems, Smart Home, Virtual Assistant
    \end{keywords}
    \section{Introduction}

@@

    As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\

@@

    These solutions resolves conflicts only between automated devices based on priorities.
    The next group of
    developers are focused on preference Rule-Based Reasoning (RBR) \cite{9}.

@@

    expectations \cite{10}.\\

@@

    environment as the Smart Home \cite{10}.\\

@@

    The component is group of modules that performs complex task that consists of a number of simple tasks.
    For example, Order Classification and Reason Classification modules are grouped to Classification component.\\

@@

    Layer is demonstrated as white rectangle with grey icon and name in it.

@@

    \footnote{Communication types and lifelines of the system is described in the Section III.}
    \begin{figure}
        \includegraphics[width=\textwidth]{arch.png}

@@

    Graphical User Interface (GUI) is expressed by 3 functional and one login pages.\\
    \begin{figure}
        \includegraphics[width=\textwidth]{mockup.png}

@@

    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.\\
    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API.
    They are JavaScript Application Programming Interfaces (API) that are used by most of the modern browsers.
    As a result, the system sends record of the user input to W3C API and it returns recognised text.
    Moreover, the system sends text to the browser of the user in such way that the browser automatically generates it into voice.

@@

    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.\\
    \begin{figure}
        \includegraphics[width=\textwidth]{ANN.png}

@@

    Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.\\

@@

    In text categorization and other similar tasks it is desirable to combine these morphological variants of the same word into one canonical form and represent it like vector that is called stemmed version.\\

@@

    The most possible class is the classification answer of the neural network.\\

@@

    1000 iterations of Backpropogation training algorithm.\\

@@

    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.\\

@@

    The Backpropagation learning rule based on supervised learning was used \cite{14}.
    In order to train neural network, a set of training documents and a specification of the pre-defined categories the
    documents belong to are required.
    Training and testing sets were created specially for this experiment.\\
    Rule-Based Reasoner receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
    Core of the Rule-Based Reasoner is the set of if-else rules.
    Firstly, RBR checks the status of the device and compares it with order.
    Secondly, it checks is there conflict between user command and rule.
    If there is a conflict it executes Case-Based Reasoner (CBR).\\
    CBR is an artificial intelligence approach to determine a similarity amongst a set of cases.
    CBR is the foundation of the many intelligent systems.

@@

    CBR is based on a suggestion that the similar cases have similar solution \cite{7}.\\
    Most of the CBR systems uses k-nearest neighbour algorithm.
    The accuracy of this classification algorithm seriously depends on the metrics or system of measurement used to compute distances between different cases.
    The nearest neighbour algorithm determines the similarity or dissimilarity of a new case with the case base and follows a cyclical process of Retrieve-Reuse-Revise-Retain.
    In our case inputs to the system are in different systems of measurements.
    Cases in the system are build on preferences and priority of users of the system.
    Both two variables have different basis.
    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.\\

@@

    Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.\\

@@

    \begin{figure}
        \includegraphics[width=0.7\textwidth]{UML.png}

@@

    Next, system sends classified order to the RBR (1.5) and checks it`s context (1.6 - 1.9).

@@

    Next, it informs the user about conflict (2.2 - 2.4) and wait command.

@@

    After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).\\

@@

    Furthermore, they were provided with additional text box under each question to justify their answers.\\
    The majority of the responses were positive \footnote{83 of 91 quantitative answers are positive, 5 neutral and 3 negative.}
    and the average of the all answers are higher the "Good" level (3 and more) except "Conflict Resolution" question, which

@@

    Second, changing the input matrix formulation might be solution.\\

@@

    develop adaptive context aware conflict resolution system based on Case-Based Reasoner.
    The validation tests feedback is positive.\\

@@

    a case to the database of Case-Based Reasoner.

@@

    increase accuracy of the Case-Based Reasoner.\\

@@

        \bibitem {5}
        Hadj, R., Hamon, C., Chollet, S., Vega, G., Lalanda, P.: Context-based conflict management in pervasive platforms. 2017 IEEE International Conference on Pervasive Computing and Communications Workshops (PerCom Workshops). (2017).

        \bibitem {6}
        Kabir, M., Hoque, M., Seo, H., Yang, S.: Machine Learning Based Adaptive Context-Aware System for Smart Home Environment, https://pdfs.semanticscholar.org/8cf5/fe5062727744f5429bb34d9c0bd24f439ee6.pdf.

@@

        \bibitem {8}
        Mayer, S., Inhelder, N., Verborgh, R., Van de Walle, R., Mattern, F.: Configuration of smart environments made simple: Combining visual modeling with semantic metadata and reasoning. 2014 International Conference on the Internet of Things (IOT). (2014).

        \bibitem {9}
        Nurgaliyev, K., Mauro, D., Khan, N., Augusto, J.: Improved Multi-user Interaction in a Smart Environment Through a Preference-Based Conflict Resolution Virtual Assistant. 2017 International Conference on Intelligent Environments (IE). (2017).

        \bibitem {10}
        Oguego, C., Augusto, J., Muñ`oz, A., Springett, M.: A survey on managing users’ preferences in ambient intelligence. Universal Access in the Information Society. (2017).

@@

        \bibitem {12}
        Ospan, B.: Simulation of a Simple Bio-Mimetic Robot with Neuromorphic Control System and Optimization Based on the Genetic Algorithm. International Journal of Innovations in Engineering and Technology. 8, 59-65 (2017).
        \bibitem {13}
        Portet, F., Vacher, M., Golanski, C., Roux, C., Meillon, B.: Design and evaluation of a smart home voice interface for the elderly: acceptability and objection aspects. Personal and Ubiquitous Computing. 17, 127-144 (2011).

>>>>

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{llncsdoc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{Images/}}
%
\begin{document}
    \title{Context Aware Virtual Assistant with
    Case-Based Conflict Resolution in
    Multi-User Smart Home Environment}
    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Quinde \inst{2} \inst{3} \and Kenzhegali Nurgaliyev \inst{1}}
    \institute{Dept. of Information Technology, Kazakh University of Technology and Business, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
    \and Dept. of Computer Science, Middlesex University, UK \\ \email{{{N.X.Khan,J.Augusto}@mdx.ac.uk}, {MQ093@live.mdx.ac.uk}}
    \and Dept. of Industrial and Systems Engineering, Universidad de Piura, Peru\\
    \email{mario.quinde@udep.pe}}
    \maketitle
    \begin{abstract}
        In this work we will examine and develop a Virtual Assistant that is used as a control
        interface of the Smart Home environment in the Middlesex University laboratory.
        Specifically, the system is
        constructed to give multiple users ability to control devices by voice or text commands through the dialogue
        interface.
        The main purpose of the research is to create user friendly interface with adaptive context aware
        Case-Based conflict resolution system.
        In addition, Artificial Neural Networks were used to classify user inputs to implement natural dialogue.
        Further, a set of random double-blinded
        evaluation tests were established.
    \end{abstract}
    \begin{keywords}
        Case-Based Reasoning, Context Awareness, Multiple User systems, Smart Home, Virtual Assistant
    \end{keywords}
    %
    \section{Introduction}
    %

@@

    As a consequence, majority of the researches is aimed to develop systems that helps alone living users.

@@

    The next group is focused on preference Rule-Based Reasoning (RBR) \cite{9}.

@@

    expectations \cite{10}.

@@

    environment as the Smart Home \cite{10}.

@@

    The component is a group of modules that performs complex task that consists of a number of simple tasks.

@@

    Layer is a white rectangle with grey icon and name in it.

@@

    \begin{figure} \centering
        \includegraphics[trim=left botm right top, width=\textwidth, clip]{arch.png}

@@

    Graphical User Interface (GUI) is expressed by 3 functional and one login pages.

@@

    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.
    \begin{figure} \centering \centering
        \includegraphics[trim=left botm right top, width=\textwidth, clip]{mockup.png}

@@

    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.
    \begin{figure} \centering \centering
        \includegraphics[trim=left botm right top, width=\textwidth, clip]{ANN.png}

@@

    Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.

@@

    In text categorization and other similar tasks it is desirable to combine these morphological variants of the same word into one canonical form and represent it like vector that is called stemmed version.

@@

    The most possible class is the classification answer of the neural network.

@@

    1000 iterations of Backpropogation training algorithm  \cite{14}.\\

@@

    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.

@@

    Rule-Based Reasoner (RBR) receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
    If there is a conflict it executes Case-Based Reasoner (CBR).
    CBR is an artificial intelligence approach to determine a similarity among a set of cases.

@@

    CBR is based on a suggestion that the similar cases have similar solution \cite{7}.

@@

    Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.

@@

    \begin{figure} \centering
        \includegraphics[trim=left botm right top, width=0.7\textwidth, clip]{UML.png}

@@

    System sends classified order to the RBR (1.5) and checks it`s context (1.6 - 1.9).

@@

    Conflict Resolution scenario starts with informing the user about a conflict (2.2 - 2.4).

@@

    After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).

@@

    The majority of the responses were positive, where 83 of 91 quantitative answers are positive, 5 neutral and 3 negative.
    An average of the all answers are higher then the "Good" level (3 and more) except "Conflict Resolution" question, which

@@

    Second, changing the input matrix might be solution.

@@

    develop adaptive context aware conflict resolution system based on CBR.
    The validation tests are positive.\\

@@

    a case to the database of CBR.

@@

    increase accuracy.\\

@@

        \bibitem {5}
        Hadj, R., Hamon, C., Chollet, S., Vega, G., Lalanda, P.: Context-based conflict management in pervasive platforms. 2017 IEEE Int. Conf. on Pervasive Computing and Communications Workshops (PerCom Workshops). (2017).

        \bibitem {6}
        Kabir, M., Hoque, M., Seo, H., Yang, S.: Machine Learning Based Adaptive Context-Aware System for Smart Home Environment.

@@

        \bibitem {8}
        Mayer, S., Inhelder, N., Verborgh, R., Van de Walle, R., Mattern, F.: Configuration of smart environments made simple: Combining visual modeling with semantic metadata and reasoning. 2014 Int. Conf. on the Internet of Things (IOT). (2014).

        \bibitem {9}
        Nurgaliyev, K., Mauro, D., Khan, N., Augusto, J.: Improved Multi-user Interaction in a Smart Environment Through a Preference-Based Conflict Resolution Virtual Assistant. 2017 Int. Conf. on Intelligent Environments (IE). (2017).

        \bibitem {10}
        Oguego, C., Augusto, J., Muñoz, A., Springett, M.: A survey on managing users’ preferences in ambient intelligence. Universal Access in the Information Society. (2017).

@@

        \bibitem {12}
        Ospan, B.: Simulation of a Simple Bio-Mimetic Robot with Neuromorphic Control System and Optimization Based on the Genetic Algorithm. Int. Journal of Innovations in Engineering and Technology. 8, 59-65 (2017).
        \bibitem {13}
        Portet, F., Vacher, M., Golanski, C., Roux, C., Meillon, B.: Design and evaluation of a smart home voice interface for the elderly: acceptability and objection aspects. Personal and Ubiquitous Computing. 17, 127-144 (2011).
